Analyzing Geographic and Demographic Patterns of Homelessness

### 2024-01-23 outputs/paper/paper.qmd
the first submission, render qmd to pdf

```{r}
#| include: false
#| warning: false
#| message: false

library(tidyverse)
library(palmerpenguins)
#| message: false
#| echo: false

#### Workspace set-up ####

#read in cleaned data #
cleaned_voter_statistics <- read.csv(here::here("inputs/data/cleaned_voter_statistics.csv"))
show_col_types = FALSE

#read in cleaned data #
summarized_voter_statistics <- read.csv(here::here("inputs/data/summarized_voter_statistics.csv"))
show_col_types = FALSE

#read in cleaned data #
summarized_voter_turnout <- read.csv(here::here("inputs/data/summarized_voter_turnout.csv"))
show_col_types = FALSE

#read in cleaned data #
finalized_voter_statistics <- read.csv(here::here("inputs/data/finalized_voter_statistics.csv"))
show_col_types = FALSE
```

@@

```{r}
#| eval: true
#| echo: false
#| message: false
#| warning: false
#| label: fig-ppcheckandposteriorvsprior
#| layout-ncol: 2
#| fig-cap: "Examining how the model fits, and is affected by, the data"
#| fig-subcap: ["Posterior prediction check", "Comparing the posterior with the prior"]

pp_check(first_model) +
  theme_classic() +
  theme(legend.position = "bottom")

posterior_vs_prior(first_model) +
  theme_minimal() +
  scale_color_brewer(palette = "Set1") +
  theme(legend.position = "bottom") +
  coord_flip()
```

>>>>

```{r}
#| include: false
#| warning: false
#| message: false
```

@@

```{r}
#| eval: true
#| echo: false
#| message: false
#| warning: false

```
